---
title: "Day 5 morning session"
author: "Marina Kochuten"
format: html
editor_options: 
  chunk_output_type: console
execute: 
  warning: false
---

```{r}
#| warning: false
#| message: false
# load libraries ----
library(tidyverse)
```

Try using `head()`, `tail()`, and `dim()` on the `dplyr::starwars` data frame:

```{r}
#| include: false
# do some data exploration on the starwars df ----
head(starwars)
tail(starwars)
dim(starwars)
```

- Create a ggplot (scatterplot) of character mass (y-axis) and height (x-axis)
- Update color of the points so that color changes based on the value of `mass`
- 

```{r}
#| warning: false
#| echo: false
ggplot(data = starwars, aes(x = height, 
                            y = mass, 
                            color = mass)) +
  geom_point() +
  labs(x = "Height (cm)", 
       y = "Mass (kg)",
       title = "Here is my title")
```

 - create a histrogram of character heights
 - update the fill color (`fill`) to purple and the borders of each bin (`color`) to orange
 - update axis labels
 - update your code chunk options so that ony your code and output graph appear in the rendered doc

```{r}
#| warning: false
#| message: false

ggplot(data = starwars, aes(x = height)) +
  geom_histogram(color = "orange", fill = "purple")


```


```{r}
sw_height_mean <- round(mean(starwars$height, na.rm = TRUE), 3)
sw_height_median <- median(starwars$height, na.rm = TRUE)
sw_height_var <- var(starwars$height, na.rm = TRUE)
sw_height_sd <- sd(starwars$height, na.rm = TRUE)
```

The mean height of starwars characters is `r sw_height_mean`



